Dependent Object Types

### 2012-09-17 doc/fool/article.tex
new abstract

\begin{abstract}
We propose a new type-theoretic foundation of Scala and languages like
it: the Dependent Object Types (DOT) calculus. DOT models Scala's
path-dependent types, abstract type members and its mixture of nominal
and structural typing through the use of refinement types.

DOT does not precisely describe what's currently in Scala: it is more
normative than descriptive, since our goal is to explore
simplifications and unifications of concepts in the type system. In
particular, DOT unifies Scala's constructs for type members, and
provides classical intersection and union types, which simplify
Scala's compound types and glb/lub computations.

>>>>

\begin{abstract}
We propose a new type-theoretic foundation of Scala and languages like
it: the Dependent Object Types (DOT) calculus. DOT models Scala's
path-dependent types, abstract type members and its mixture of nominal
and structural typing through the use of refinement types. The core
formalism makes no attempt to model inheritance and mixin
composition. DOT normalizes Scala's type system by unifying the
constructs for type members and by providing classical intersection
and union types which simplify Scala's compound types and glb/lub
computations.
